Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-16 publication_materials/ms_rbc.tex
Misc. changes

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$. 
    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
    For large $\Ra$, the boundary layers admit small scale features, requiring more basis functions (higher resolution).
    It follows that the minimum $z$ length scale to agrees with the boundary layer height $\delta$. 
    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$ \note{There has to be published work on this length scale agreement}.}
    \label{fig:del_inv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim\Ra^{1/3}$. 
    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$. 
    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
    For large $\Ra$, the boundary layers admit small scale features, requiring more basis functions (higher resolution).
    It follows that the minimum $z$ length scale to agrees with the boundary layer height $\delta$. 
    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$.}
    \label{fig:del_inv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
    All datasets obey power-law relationships, with the MSTE and ECS scaling like $\Nu \sim\Ra^{1/3}$. 
    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. 
    This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}
